---
title: "Phoenix Tracker"
site: bookdown::bookdown_site
github-repo: altaf-ali/phoenix_tracker
---

# Introduction

This project analyzes event data from the [Phoenix Data Project](http://phoenixdata.org)

## Getting Started

Load the necessary packages. 

```{r message=FALSE}
library(plyr)
library(yaml)
library(tidyverse)
```

## LoadingDataset

The `phoenix.R` script provides a function that simplifies downloading and loading the dataset. We set the start date to the beginning of the year and load the dataset. The `phoenix_load()` function downloads the dataset if necessary.

```{r message=FALSE, results='hide'}
source('R/phoenix.R')

config <- yaml.load_file("config.yml")
events <- phoenix_load(config, start_date = "2017-01-01")
```

Let's see what's in the dataset

```{r}
str(events)
```

Show selected columns

```{r}
events %>%
  select(Date, SourceActorFull, TargetActorFull, EventCode, LocationName) %>%
  head()
```


----

*Last Updated: `r format(Sys.time(), "%b %d, %Y %l:%M %p")`*
